The Name of the Title is Hope

### 2019-03-26 emsoft-2019/main.tex
"Main file" now called main.tex

While $\varepsilon_{A/D}$ is intrinsic in the capabilities of the device, $\varepsilon_{Q}$ depends on the precision used to store the boundaries. This second error can be regulated based on a trade-off among accuracy of the storage and memory save.

The total size of the \texttt{tube} is then:
\begin{equation}\label{eq:epsilontot}
\varepsilon=\varepsilon_{A/D}+\varepsilon_{Q}
\end{equation}
\section{Finite Precision Implementation}
The output of the controller can be affected by two main errors: (i) the first one happens when the controller chooses the wrong activation function because of $\varepsilon$ in (\ref{eq:epsilontot}), while the second one (ii) is the approximation error deriving from the finite precision arithmetic used to compute the activation function itself.

The effect of selecting the wrong activation function are the same as instability in the conditional switch reported in Listing \ref{lst:caseof}: suppose an hypothetic scenario where all the measurements were done in infinite precision and without any uncertainty, the controller $i$ would be activated, but because of these limitations actually $j$ is selected. The resulting error is then the difference between the two branches $i$ and $j$ in Listing \ref{lst:caseof}.

The system has to be robust against a mistake in choosing controller $i$ instead of $j$ only when \qstatevarmath falls into the \texttt{tube} between $i$ and $j$, and not for all the points in the two regions.

In the following, we assume $i$ and $j$ are the index of two generic regions in \statespace:

%\begin{equation}
\begin{flalign}
\label{eq:maximization}
&\max_{\forall i,j\;|\;neighbour(i,j)}|u_{i}-u_{j}| = \\
&\max_{\forall i,j\;|\;neighbour(i,j)}|F_{i}\statevar+G_{i} - (F_{j}\statevar+G_{j})|
\end{flalign}
%\end{equation}

Because of the linearity of the function $U_{i}-U_{j}$, and because of the convexity of regions $i$, $j$ it is enough to evaluate function (\ref{eq:maximization}) at the corners of the \texttt{tube}.

@@

In formula $\exists\; m,n \;$such that:
\begin{equation}
(H_{i}\statevar-K_{j})_{m} = (H_{j}\statevar-K_{j})_{n}
\end{equation}
where $m$ and $n$ are the index of the two matching borders. We label $border_{i,j}$ the matching border shared among the two regions.

Starting from the equation of $border_{i,j}$, we delimit the geometrical space where it makes sense to compute (\ref{eq:maximization}) with: 
\begin{equation}
\begin{aligned}
border_{i,j} >= -\varepsilon\\
border_{i,j} <= \varepsilon
\end{aligned} 
\end{equation}
We call such geometrical space the \texttt{tube} between $i$ and $j$.

@@

\section{Precision Tuning}
In formula (\ref{eq:epsilontot}), the equation for $\varepsilon$ contains: $\varepsilon_{A/D}$ that is the error introduced by the analog-digital conversion, and $\varepsilon_{Q}$ generated by the quantization of hyperplanes H and K in a finite number of bits.
This $\varepsilon_{Q}$ can be tuned based on memory availability in the micro-controller.
The rule for $\varepsilon_{Q}$ is the following:
\begin{equation}\label{eq:quantizationlines}
\varepsilon_{Q} > (H-(\hat{H})_{p})\qstatevar+(K-(\hat{K})_{p})
\end{equation}
This inequality assures that the distance between any hyperplane represented in infinite precision, and the counter-part quantized in p bits, is bounded by $\varepsilon_{Q}$.

Our goal is to solve (\ref{eq:quantizationlines}) with respect to p: find the minimal-precision for all the coefficients such that the inequality holds.

@@

To solve (\ref{eq:quantizationlines}) we used Daisy: a static analyzer for both floating-point and fixed-point expressions, able to provide a sound upper-bound to the maximal approximation error of an expression with respect to its real (infinite precision) counterpart. Because the magnitude of the round-off error depends on the range of input variable, all variables encoded in Daisy have to be bounded. 
Since the state variable \statevarmath is bounded, and F,G,H,K are vectors of constants, we can rely on Daisy for this verification step.

@@

\begin{flalign}
\label{eq:deltaminusmax}
&delta - \Big(\max_{\forall i,j\;|\;neighbour(i,j)}|u_{i}-u_{j}|\Big)>=\\
& \max_{\forall\;\regionimath{i}\;in\;\statespace} err(u_{i})_{p}\nonumber
\end{flalign}
We want to point out that the left side of the inequality is not parametrized in p. Only the right size of (\ref{eq:deltaminusmax}) actually depends on the precision p. Again, we encode (\ref{eq:deltaminusmax}) in Daisy to detect what is the minimal precision that still satisfy the inequality.

@@

Even if it possible to assign value zero to delta\cite{imperial}, we do not encourage such initialization: it is going to fail the analysis at least once, because the error in (\ref{eq:maxfperror}) is going to be greater than zero (even in case (\ref{eq:maximization}) is zero). A better initialization would be to set delta to an arbitrary small value, slightly greater than zero.

@@

In case the conditional is verified,
the precision tuning phase starts.
For the precision tuning of activation functions, we allow an error that is bounded by \texttt{max\_err}. This is because we still need to satisfy (\ref{eq:delta}).
On the other hand, the quantization of polytopes borders (the region bounds in \statespace) can produce an error that is at most $\varepsilon_{Q}$, in this way we satisfy 
(\ref{eq:quantizationlines}).

In case the conditional fails and \texttt{maxUij} is greater than delta, the controller needs to be re-designed with a robustness value that is at least equal to the current value of \texttt{maxUij}. The same consideration done for the initialization values holds also here: the constant $\varepsilon_{SAFE}$ is used to relax the value delta for the controller, to a slight greater value than \texttt{maxUij}. In this way, we aim to give some space to the precision tuning phase in the next iteration of the loop. Otherwise, in case of $\varepsilon_{SAFE}$ equal to zero, the next iteration of the precision tuning phase is going to require unnecessarily wide precision values p, usually greater than 32 bits. 
We remark that the point of the analysis is to find a low precision configuration for bounds and activation functions.
In case the analysis outputs a precision greater than 32bits, we fail in our goal.
Then, with a minimal alteration to the upper bound of delta, we sensibly reduced the precision needed for $F$ and $G$, with respect to the standard 32 bits.

>>>>

While $\varepsilon_{A/D}$ is intrinsic in the capabilities of the device, $\varepsilon_{Q}$ depends on the precision used to store the boundaries. This second error can be regulated based on a trade-off among accuracy of the storage and memory save~\cite{memoryMPC}.

The total size of the \texttt{tube} is then:
\begin{equation}\label{eq:epsilontot}
\varepsilon=\varepsilon_{A/D}+\varepsilon_{Q}
\end{equation}
\section{Finite Precision Implementation}
The output of the controller can be affected by two main errors: (i) the controller chooses the wrong activation function because of $\varepsilon$ in (\ref{eq:epsilontot}), while (ii) is the approximation error deriving from the finite precision arithmetic used to compute the activation function itself~\cite{imperialrmpc}.

The effect of selecting the wrong activation function are similar to instability in the switch reported in Listing \ref{lst:caseof}. Suppose an hypothetic scenario where all the measurements were done in infinite precision and without any uncertainty: the controller $i$ would be activated.

Instead, because of these limitations controller $j$ is selected. The resulting error is then the difference between the output of the two branches $i$ and $j$.

The system has to be robust against a mistake in choosing controller $i$ instead of $j$ (or vice-versa) only when \qstatevarmath falls into the \texttt{tube} between $i$ and $j$, and not for all the points in the two regions.

In the following, we assume $i$ and $j$ are the index of two generic regions in \statespace:
\begin{flalign}
\label{eq:maximization}
&\max_{\forall i,j\;|\;neighbour(i,j)}|u_{i}-u_{j}| = \\
&\max_{\forall i,j\;|\;neighbour(i,j)}|F_{i}\statevar+G_{i} - (F_{j}\statevar+G_{j})|\nonumber
\end{flalign}

Because of the linearity of the function $u_{i}-u_{j}$, and because of the convexity of the regions $i$, $j$ it is enough to evaluate function (\ref{eq:maximization}) at the corners of the \texttt{tube}.

@@

In formula $\exists\; m,n \;$such that:
\begin{equation}
(H_{i}\statevar-K_{j})_{m} = (H_{j}\statevar-K_{j})_{n}
\end{equation}
where $m$ and $n$ are the index of the two matching borders. We label with $border_{i,j}$ the matching border shared among the two regions.

Starting from the equation of $border_{i,j}$, we delimit the geometrical space where it makes sense to compute (\ref{eq:maximization}) with: 
\begin{equation}
\begin{aligned}
border_{i,j} >= -\varepsilon\\
border_{i,j} <= \varepsilon
\end{aligned} 
\end{equation}
where $\varepsilon$ is defined in (\ref{eq:epsilontot}).

We call such geometrical space the \texttt{tube} between $i$ and $j$.

@@

\section{Precision Tuning}
In formula (\ref{eq:epsilontot}), the equation for $\varepsilon$ contains: $\varepsilon_{A/D}$ that is the error introduced by the analog-digital conversion, and $\varepsilon_{Q}$ that is generated by the quantization of hyperplanes $H\statevar<=K$ in a finite number of bits.
This $\varepsilon_{Q}$ can be tuned based on memory availability in the micro-controller.
The rule for $\varepsilon_{Q}$ is the following:
\begin{equation}\label{eq:quantizationlines}
\varepsilon_{Q} > (H-(\hat{H})_{p})\qstatevar+(K-(\hat{K})_{p})
\end{equation}
This inequality assures that the distance between any hyperplane represented in infinite precision, and its counter-part quantized in p bits, is bounded by $\varepsilon_{Q}$.

Our goal is to solve (\ref{eq:quantizationlines}) with respect to p: find the minimal-precision p such that the inequality holds.

@@

To solve (\ref{eq:quantizationlines}) we used Daisy: a static analyzer for finite precision expressions, able to provide a sound upper-bound to the maximal approximation error of an expression with respect to its real (infinite precision) counterpart. Since the magnitude of the round-off error depends on the range of input variables, any variable encoded in Daisy has to be bounded.

Since the state variable \statevarmath is bounded, and F,G,H, and K are vectors of constants, we can rely on Daisy for this verification step.

@@

\begin{flalign}
\label{eq:deltaminusmax}
&delta - \Big(\max_{\forall i,j\;|\;neighbour(i,j)}|u_{i}-u_{j}|\Big)>=\\
& \max_{\forall\;\regionimath{i}\;in\;\statespace} err(u_{i})_{p}\nonumber
\end{flalign}
We want to point out that the left side of the inequality is not parametrized in p. Only the right size of (\ref{eq:deltaminusmax}) actually depends on the precision p. We encode the inequality (\ref{eq:deltaminusmax}) in Daisy, to detect what is the minimal precision that satisfy the inequality.

@@

Even if it possible to assign value zero to delta~\cite{imperialrmpc}, we do not encourage such initialization: it is going to fail the analysis at least once because the error in (\ref{eq:maxfperror}) is going to be greater than zero (even in case (\ref{eq:maximization}) is zero). A better initialization would be to set delta to an arbitrary small value, slightly greater than zero.

@@

In case the conditional statement is verified,
the precision tuning phase starts.
For the precision tuning of activation functions, we allow an error that is bounded by \texttt{max\_err}. This is because we still need to satisfy (\ref{eq:delta}).
On the other hand, the quantization of polytopes borders (the region bounds in \statespace) can produce an error that is at most $\varepsilon_{Q}$, in this way we satisfy 
(\ref{eq:quantizationlines}).

In case the conditional fails and \texttt{maxUij} is greater than delta, the controller needs to be re-designed with a robustness value that is at least equal to the current value of \texttt{maxUij}. The same consideration done for the initialization of input parameters holds also here: the constant $\varepsilon_{SAFE}$ is used to relax the value delta for the controller, to a value slightly greater than \texttt{maxUij}. In this way, we aim to give some space to the precision tuning phase in the next iteration of the loop. Otherwise, in case of $\varepsilon_{SAFE}$ equal to zero, the next iteration of the precision tuning phase is going to require unnecessarily wide precision values p, usually greater than 32 bits. 
We remark that the point of the analysis is to find a low precision configuration for bounds and activation functions: in case the analysis outputs a precision greater than 32bits, we fail in our goal.
Then, with a minimal alteration to the upper bound of delta, we sensibly reduce the precision needed for $F$ and $G$, with respect to the standard 32 bits precision.
